### 2023-10-11 main.tex
Update main.tex

To a configuration $\bm{\xi}$ of the configuration space  \eqref{dualStateSpace} of a dual process we associate the vector
\begin{equation}
    |\bm{\xi}\rangle=\bigotimes_{x\in V}\left(|\xi_{1}^{x},\ldots,\xi_{N}^{x}\rangle\otimes |\xi_{1}^{u(x)},\ldots,\xi_{N}^{u(x)}\rangle\right)\dt
\end{equation}
The Hamiltonian of the dual process reads
\begin{equation}\label{DualHamiltonian}
    \widetilde{H}=\sum_{x,y\in \mathcal{E}}\omega_{x,y}\mathcal{H}_{x,y}+\sum_{x\in V}\Gamma_{x}\widetilde{H}_{x}
\end{equation}
where $\mathcal{H}_{x,y}$ is the one defined in \eqref{edgeHamiltonian}, while 
\begin{equation}\label{siteDualHamiltonian}
    \widetilde{H}_{x}=|\alpha^{x}|\sum_{a=1}^{N-1}\left((A^{\dagger})_{a}^{u(x)}\,E_{Na}^{x}-E_{aa}^{x}\right)\dt
\end{equation}
Here we introduced bosonic creation operator $A^{\dagger}$ acting on the left-hand-side as $\langle q|A^{\dagger}=\langle q+1|$ on a generic vector $\langle q|$ with $q\in \mathbb{N}_{0}$, so that in \eqref{siteDualHamiltonian} 
$(A^{\dagger})_{a}^{u(x)}$ denotes a copy of $A^{\dagger}$ acting on the extra-site $u(x)$ and on the species $a\in\{1,\ldots,N-1\}$. \\
We will show below that the Hamiltonians \eqref{OriginalHamiltonian} and \eqref{DualHamiltonian} are dual in the sense of \eqref{DualityRelation}. From an algebraic point of view, the duality matrix $D$ \eqref{dualityElements} is described as 
\begin{equation}\label{dualityMatrix}
    D=\prod_{x\in V}d_{x}\otimes \dd \;.
\end{equation}
Here
\begin{equation}\label{bulkElementDualityMatrix}
d_{x}=R_{x}\exp{(E^{x})}
\end{equation}
with 
\begin{equation}\label{Revmatrix}
    R_{x}=\sum_{n^{x}\in\Omega_{x}}\frac{\prod_{a=1}^{N}n_{a}^{x}!}{\nu!}|n_{1}^{x},\ldots,n_{N}^{x}\rangle\langle n_{1}^{x},\ldots,n_{N}^{x}|
\end{equation}
and
\begin{equation}\label{EquationEx}
E^{x}=\sum_{a=1}^{N-1}E_{aN}^{x}\,.
\end{equation}
Furthermore
\begin{equation}\label{dualityMatrix2}
\dd=\sum_{\xi_{1}^{u(x)},\ldots,\xi_{N-1}^{u(x)}=0}^{\infty}\prod_{a=1}^{N-1}\left(\rho_{a}^{x}\right)^{\xi_{a}^{u(x)}}\langle \xi_{1}^{u(x)},\ldots,\xi_{N}^{u(x)}|\dt
\end{equation}
We observe that the matrix $R_{x}$ is diagonal. Its elements are related to the inverse of the weights of the reversible measure \eqref{reversibleMeasure}. In particular, to obtain these elements, we have considered the weights of \eqref{reversibleMeasure} when all the parameters $\rho_{a}=\frac{1}{N}$. Then, the constant $\left(\frac{1}{N}\right)^{\nu}$ has been neglected, since it does not change the duality relation. This $R_{x}$ is called the ``cheap'' duality matrix and is associated to reversibility (see \cite{giardina2009duality}). \\

@@

R_{x}E_{ab}^{x}R_{x}^{-1}=&\sum_{r^{x}\in\Omega_{x}}\frac{\xi_{1}^{x}!\ldots r_{N}!}{\nu!}|\xi_{1}^{x},\ldots,\xi_{N}^{x}\rangle \langle \xi_{1}^{x},\ldots, \xi_{N}^{x}|
	\sum_{s^{x}\in \Omega_{x},}s_{b}^{x}|s_{1}^{x},\ldots,s_{a}^{x}+1,\ldots,s_{b}^{x}-1,\ldots s_{N}^{x}\rangle \langle s_{1}^{x},\ldots,s_{N}^{x}|
	\sum_{n^{x}\in\Omega_{x}}\frac{\nu!}{n_{1}!\ldots n_{N}!}|n_{1}^{x},\ldots,n_{N}^{x}\rangle \langle n_{1}^{x},\ldots, n_{N}^{x}|
 \\=&\sum_{r^{x}\in \Omega_{x}}
	\xi_{a}^{x}|\xi_{1}^{x},\ldots,\xi_{N}^{x}\rangle \langle \xi_{1}^{x},\ldots,\xi_{a}^{x}-1,\ldots,r_{b}^{x}-1,\ldots,\xi_{N}^{x}|
	\left(E_{ba}^{x}\right)^{T}
where in the up to last equation we used the orthogonality relation \eqref{ortho}. 
\paragraph{Elements of the duality matrix.}
Consider the matrix $D$ defined in \eqref{dualityMatrix}.
We aim to show that its matrix elements coincide with duality function \eqref{dualityElements}, i.e.
\begin{equation}\label{proofDualityElements}
\langle \bm{n}|D|\bm{\xi}\rangle=D(\bm{n},\bm{\xi})\qquad   \forall \bm{n}\in \Omega,\quad \bm{\xi}\in \widetilde{\Omega}\,.
Fix an arbitrary site $x\in V$, then we have that 
	 &\langle n^{x}|d_{x}\otimes \dd|\xi^{x}\rangle\\=&\langle n_{1}^{x},\ldots,n_{N}^{x}| (\exp{(E_{N1}^{x}+\ldots+E_{N\,N-1}^{x}}))^{T}R_{x}\otimes\sum_{q_{1}^{u(x)},\ldots,q_{N-1}^{u(x)}=0}^{\infty}\prod_{a=1}^{N-1}\left(\rho_{a}^{x}\right)^{q_{a}^{u(x)}}\langle q_{1}^{u(x)},\ldots,q_{N}^{u(x)}|
	 \\&|\xi_{1}^{x},\ldots,\xi_{N}^{x}\rangle \otimes |\xi_{1}^{u(x)},\ldots,\xi_{N}^{u(x)}\rangle
where we used \eqref{transpositionPropertyR}. \\
On one hand, on the extra-site $u(x)$ we have 
\sum_{q_{1}^{u(x)},\ldots,q_{N-1}^{u(x)}=0}^{\infty}\prod_{a=1}^{N-1}\left(\rho_{a}^{x}\right)^{q_{a}^{u(x)}}\langle q_{1}^{u(x)},\ldots,q_{N}^{u(x)}|\xi_{1}^{u(x)},\ldots,\xi_{N}^{u(x)}\rangle=\prod_{a=1}^{N-1}\left(\rho_{a}^{x}\right)^{\xi_{a}^{u(x)}}
where {\color{red} we used the orthogonality relation \eqref{ortho}}. 
On the other hand, on the site $x$, we have 
&\langle n_{1}^{x},\ldots,n_{N}^{x}|(\exp{(E_{N1}^{x}+\ldots+E_{N\,N-1}^{x})})^{T}R_{x}|\xi_{1}^{x},\ldots,\xi_{N}^{x}\rangle\\&= \langle  n_{1}^{x},\ldots,n_{N}^{x}|\left(\sum_{k_{1}=0}^{\infty}\frac{\left\{\left(E_{N1}^{x}\right)^{T}\right\}^{k_{1}}}{k_{1}!}\ldots\sum_{k_{N-1}=0}^{\infty}\frac{\left\{\left(E_{N\,N-1}^{x}\right)^{T}\right\}^{k_{N-1}}}{k_{N-1}!}\sum_{s\in\Omega_{x}}\frac{s_{1}^{x}!\ldots s_{N}^{x}!}{\nu!}|s_{1}^{x},\ldots,s_{N}^{x}\rangle\langle s_{1}^{x},\ldots,s_{N}^{x}|\right)
\hspace{2.cm}\qquad|\xi_{1}^{x},\ldots,\xi_{N}^{x}\rangle
\sum_{k_{1}=0}^{n_{1}^{x}}\ldots\sum_{k_{N-1}=0}^{n_{N-1}^{x}}\langle n_{1}^{x}-k_{1},\ldots,n_{N-1}^{x}-k_{N-1},n_{N}^{x}+k_{1}+\ldots+k_{N-1}|
\hspace{2.cm}\prod_{a=1}^{N-1}\left((n_{a}^{x}(n_{a}^{x}-1)\ldots (n_{a}^{x}-k_{a}+1)\right)\frac{1}{k_{1}!,\ldots,k_{N-1}!}\frac{\xi_{1}^{x}!\ldots \xi_{N}^{x}!}{\nu!}|\xi_{1}^{x},\ldots,\xi_{N}^{x}\rangle
\sum_{k_{1}=0}^{n_{1}^{x}}\ldots\sum_{k_{N-1}=0}^{n_{N-1}^{x}}\langle n_{1}^{x}-k_{1},\ldots,n_{N-1}^{x}-k_{N-1},\ldots,n_{N}^{x}+k_{1}+\ldots+k_{N-1}|\frac{n_{1}^{x}!\ldots n_{N-1}^{x}!}{(n_{1}^{x}-k_{1})!\ldots(n_{N-1}^{x}-k_{N-1})!}
\hspace{2.cm}\qquad\frac{1}{k_{1}!,\ldots,k_{N-1}!}\frac{\xi_{1}^{x}!\ldots \xi_{N}^{x}!}{\nu!}|\xi_{1}^{x},\ldots,\xi_{N}^{x}\rangle
\frac{(\nu-\sum_{a=1}^{N-1}\xi_{a}^{x})}{\nu!}\prod_{a=1}^{N-1}\frac{n_{a}^{x}!}{(n_{a}^{x}-\xi_{a}^{x})!}
where in the last equality we applied the orthogonality relations \eqref{ortho} and the fact that $\xi_{N}^{x}=\nu-\sum_{a=1}^{N-1}\xi_{a}^{x}$. Finally, by taking the product over $x\in V$ \eqref{proofDualityElements} is proved.
\paragraph{Proof of \eqref{edgeDualRealtion}.}To show this relation we need two 'ingredients'. First the existence of a similarity transformation between the Hamiltonian $\mathcal{H}_{x,y}$  and its transposed. As we will show, this similarity transformation is $R_{x}R_{y}$.  Second, the possibility of finding a symmetry for the edge Hamiltonian. Exploiting \eqref{hamiltonianCasimir}, we will search for a symmetry of the second Casimir $C_{2}$. As we will see, this symmetry is $\sum_{a=1}^{N-1}E_{aN}$ \\
We first look for the similarity between $\mathcal{H}_{x,y}$ and its transposed. Using \eqref{transpositionPropertyR} we obtain

\begin{equation}\label{transpositionPropertyH}
    \mathcal{H}_{x,y}^{T}=\left(R_{x}R_{y}\right)\mathcal{H}_{x,y}\left(R_{x}R_{y}\right)^{-1}
\end{equation}
therefore we have found the similarity transformation between $\mathcal{H}_{x,y}$ and its transposed. \\
We now look for a symmetry of $\mathcal{H}_{x,y}$, i.e. a matrix $S_{x,y}$ of the same dimension such that it satisfies 
\begin{equation}
	\mathcal{H}_{x,y}S_{x,y}=S_{x,y}\mathcal{H}_{x,y}\quad \Leftrightarrow \quad [\mathcal{H}_{x,y},S_{x,y}]=0\dt
\end{equation}
Using \eqref{hamiltonianCasimir}, we observe that $\mathcal{H}_{x,y}$ is proportional to the coproduct of the second Casimir, up to a diagonal term. Therefore, it is enough to look for a symmetry of $\Delta (C_{2})$. Using the bilinearity of the coproduct operator and the fact that $C_{2}$ belongs to the centre of the Lie algebra, it is easy to show that for any matrix $E\in gl(N)$ it holds
\begin{equation}
	[C_{2},E]=0\quad \Rightarrow\quad \left[\Delta (C_{2}),\Delta(E)) \right]=0\dt
\end{equation}
We chose 
\begin{equation}
	E=\sum_{a=1}^{N-1}E_{aN}
\end{equation}
and, for a fixed $(x,y)\in \mathcal{E}$, we define
\begin{equation}
	S_{x,y}=\exp{(\Delta^{x,y}(E))}=\exp{(E^{x})}\exp{(E^{y})}
\end{equation}
where $\Delta^{x,y}(E)$ is a copy of the coproduct acting on sites $x$ and $y$. Therefore, this operator $S_{x,y}$ satisfies
\begin{equation}\label{symmetryH}
	\left[S_{x,y},\mathcal{H}_{x,y}\right]=0
\end{equation}
i.e. it is a symmetry of $\mathcal{H}_{x,y}$. \\ Exploiting these considerations we write

>>>>

To a configuration $\bm{\xi}$ of the configuration space  \eqref{dualStateSpace} of a dual process we associate the vector
\begin{equation}
    |\bm{\xi}\rangle=\bigotimes_{x\in V}\left(|\xi_{1}^{x},\ldots,\xi_{N}^{x}\rangle\otimes |\xi_{1}^{u(x)},\ldots,\xi_{N}^{u(x)}\rangle\right)\dt
\end{equation}
The Hamiltonian of the dual process reads
\begin{equation}\label{DualHamiltonian}
    \widetilde{H}=\sum_{x,y\in \mathcal{E}}\omega_{x,y}\mathcal{H}_{x,y}+\sum_{x\in V}\Gamma_{x}\widetilde{H}_{x}
\end{equation}
where $\mathcal{H}_{x,y}$ is the one defined in \eqref{edgeHamiltonian}, while 
\begin{equation}\label{siteDualHamiltonian}
    \widetilde{H}_{x}=|\alpha^{x}|\sum_{a=1}^{N-1}\left((A^{\dagger})_{a}^{u(x)}\,E_{Na}^{x}-E_{aa}^{x}\right)\dt
\end{equation}
Here we introduced bosonic creation operator $A^{\dagger}$ acting on the left-hand-side as $\langle q|A^{\dagger}=\langle q+1|$ on a generic vector $\langle q|$ with $q\in \mathbb{N}_{0}$, so that in \eqref{siteDualHamiltonian} 
$(A^{\dagger})_{a}^{u(x)}$ denotes a copy of $A^{\dagger}$ acting on the extra-site $u(x)$ and on the species $a\in\{1,\ldots,N-1\}$. \\

We will show below that the Hamiltonians \eqref{OriginalHamiltonian} and \eqref{DualHamiltonian} are dual in the sense of \eqref{DualityRelation}. From an algebraic point of view, the duality matrix $D$ \eqref{dualityElements} is described as 
\begin{equation}\label{dualityMatrix}
    D=\prod_{x\in V}d_{x}\otimes \dd \;.
\end{equation}
Here
\begin{equation}\label{bulkElementDualityMatrix}
d_{x}=R_{x}\exp{(E^{x})}
\end{equation}
with 
\begin{equation}\label{Revmatrix}
    R_{x}=\sum_{n^{x}\in\Omega_{x}}\frac{\prod_{a=1}^{N}n_{a}^{x}!}{\nu!}|n_{1}^{x},\ldots,n_{N}^{x}\rangle\langle n_{1}^{x},\ldots,n_{N}^{x}|
\end{equation}
and
\begin{equation}\label{EquationEx}
E^{x}=\sum_{a=1}^{N-1}E_{aN}^{x}\,.
\end{equation}
Furthermore
\begin{equation}\label{dualityMatrix2}
\dd=\sum_{\xi_{1}^{u(x)},\ldots,\xi_{N-1}^{u(x)}=0}^{\infty}\prod_{a=1}^{N-1}\left(\rho_{a}^{x}\right)^{\xi_{a}^{u(x)}}\langle \xi_{1}^{u(x)},\ldots,\xi_{N}^{u(x)}|\dt
\end{equation}
We observe that the matrix $R_{x}$ is diagonal. Its elements are related to the inverse of the weights of the reversible measure \eqref{reversibleMeasure}. In particular, to obtain these elements, we have considered the weights of \eqref{reversibleMeasure} when all the parameters $\rho_{a}=\frac{1}{N}$. Then, the constant $\left(\frac{1}{N}\right)^{\nu}$ has been neglected, since it does not change the duality relation. This $R_{x}$ is called the ``cheap'' duality matrix and is associated to reversibility (see \cite{giardina2009duality}). \\

@@

\begin{align*}
R_{x}E_{ab}^{x}R_{x}^{-1}=&\sum_{r^{x}\in\Omega_{x}}\frac{\xi_{1}^{x}!\ldots r_{N}!}{\nu!}|\xi_{1}^{x},\ldots,\xi_{N}^{x}\rangle \langle \xi_{1}^{x},\ldots, \xi_{N}^{x}|
	\\&
	\sum_{s^{x}\in \Omega_{x},}s_{b}^{x}|s_{1}^{x},\ldots,s_{a}^{x}+1,\ldots,s_{b}^{x}-1,\ldots s_{N}^{x}\rangle \langle s_{1}^{x},\ldots,s_{N}^{x}|
	\\&
	\sum_{n^{x}\in\Omega_{x}}\frac{\nu!}{n_{1}!\ldots n_{N}!}|n_{1}^{x},\ldots,n_{N}^{x}\rangle \langle n_{1}^{x},\ldots, n_{N}^{x}|
 \\=&\sum_{r^{x}\in \Omega_{x}}
	\xi_{a}^{x}|\xi_{1}^{x},\ldots,\xi_{N}^{x}\rangle \langle \xi_{1}^{x},\ldots,\xi_{a}^{x}-1,\ldots,r_{b}^{x}-1,\ldots,\xi_{N}^{x}|
	\\=&
	\left(E_{ba}^{x}\right)^{T}
\end{align*}
where in the up to last equation we used the orthogonality relation \eqref{ortho}. 
\end{comment}
\paragraph{Elements of the duality matrix.}
Consider the matrix $D$ defined in \eqref{dualityMatrix}.
We aim to show that its matrix elements coincide with duality function \eqref{dualityElements}, i.e.
\begin{equation}\label{proofDualityElements}
\langle \bm{n}|D|\bm{\xi}\rangle=D(\bm{n},\bm{\xi})\qquad   \forall \bm{n}\in \Omega,\quad \bm{\xi}\in \widetilde{\Omega}\,.
\end{equation}
Fix an arbitrary site $x\in V$, then we have that 
\begin{align*}
	 &\langle n^{x}|d_{x}\otimes \dd|\xi^{x}\rangle\\=&\langle n_{1}^{x},\ldots,n_{N}^{x}| (\exp{(E_{N1}^{x}+\ldots+E_{N\,N-1}^{x}}))^{T}R_{x}\otimes\sum_{q_{1}^{u(x)},\ldots,q_{N-1}^{u(x)}=0}^{\infty}\prod_{a=1}^{N-1}\left(\rho_{a}^{x}\right)^{q_{a}^{u(x)}}\langle q_{1}^{u(x)},\ldots,q_{N}^{u(x)}|
	 \\&|\xi_{1}^{x},\ldots,\xi_{N}^{x}\rangle \otimes |\xi_{1}^{u(x)},\ldots,\xi_{N}^{u(x)}\rangle
\end{align*}
where we used \eqref{transpositionPropertyR}. \\
On one hand, on the extra-site $u(x)$ we have 
\begin{align*}
\sum_{q_{1}^{u(x)},\ldots,q_{N-1}^{u(x)}=0}^{\infty}\prod_{a=1}^{N-1}\left(\rho_{a}^{x}\right)^{q_{a}^{u(x)}}\langle q_{1}^{u(x)},\ldots,q_{N}^{u(x)}|\xi_{1}^{u(x)},\ldots,\xi_{N}^{u(x)}\rangle=\prod_{a=1}^{N-1}\left(\rho_{a}^{x}\right)^{\xi_{a}^{u(x)}}
\end{align*}
where {\color{red} we used the orthogonality relation \eqref{ortho}}. 
On the other hand, on the site $x$, we have 
\begin{align*}
&\langle n_{1}^{x},\ldots,n_{N}^{x}|(\exp{(E_{N1}^{x}+\ldots+E_{N\,N-1}^{x})})^{T}R_{x}|\xi_{1}^{x},\ldots,\xi_{N}^{x}\rangle\\&= \langle  n_{1}^{x},\ldots,n_{N}^{x}|\left(\sum_{k_{1}=0}^{\infty}\frac{\left\{\left(E_{N1}^{x}\right)^{T}\right\}^{k_{1}}}{k_{1}!}\ldots\sum_{k_{N-1}=0}^{\infty}\frac{\left\{\left(E_{N\,N-1}^{x}\right)^{T}\right\}^{k_{N-1}}}{k_{N-1}!}\sum_{s\in\Omega_{x}}\frac{s_{1}^{x}!\ldots s_{N}^{x}!}{\nu!}|s_{1}^{x},\ldots,s_{N}^{x}\rangle\langle s_{1}^{x},\ldots,s_{N}^{x}|\right)
\\&
\hspace{2.cm}\qquad|\xi_{1}^{x},\ldots,\xi_{N}^{x}\rangle
%\\&=
%\sum_{k_{1}=0}^{n_{1}^{x}}\ldots\sum_{k_{N-1}=0}^{n_{N-1}^{x}}\langle n_{1}^{x}-k_{1},\ldots,n_{N-1}^{x}-k_{N-1},n_{N}^{x}+k_{1}+\ldots+k_{N-1}|
%\\&
%\hspace{2.cm}\prod_{a=1}^{N-1}\left((n_{a}^{x}(n_{a}^{x}-1)\ldots (n_{a}^{x}-k_{a}+1)\right)\frac{1}{k_{1}!,\ldots,k_{N-1}!}\frac{\xi_{1}^{x}!\ldots \xi_{N}^{x}!}{\nu!}|\xi_{1}^{x},\ldots,\xi_{N}^{x}\rangle
\\&=
\sum_{k_{1}=0}^{n_{1}^{x}}\ldots\sum_{k_{N-1}=0}^{n_{N-1}^{x}}\langle n_{1}^{x}-k_{1},\ldots,n_{N-1}^{x}-k_{N-1},\ldots,n_{N}^{x}+k_{1}+\ldots+k_{N-1}|\frac{n_{1}^{x}!\ldots n_{N-1}^{x}!}{(n_{1}^{x}-k_{1})!\ldots(n_{N-1}^{x}-k_{N-1})!}
\\& 
\hspace{2.cm}\qquad\frac{1}{k_{1}!,\ldots,k_{N-1}!}\frac{\xi_{1}^{x}!\ldots \xi_{N}^{x}!}{\nu!}|\xi_{1}^{x},\ldots,\xi_{N}^{x}\rangle
\\&=
\frac{(\nu-\sum_{a=1}^{N-1}\xi_{a}^{x})}{\nu!}\prod_{a=1}^{N-1}\frac{n_{a}^{x}!}{(n_{a}^{x}-\xi_{a}^{x})!}
\end{align*}
where we used the definitions of the action of $E_{ab}$ {\color{red} and the orthogonality relations \eqref{ortho}}, together with the fact that $\xi_{N}^{x}=\nu-\sum_{a=1}^{N-1}\xi_{a}^{x}$. 
Finally, by taking the product over $x\in V$ \eqref{proofDualityElements} is proved.
\begin{flushright}
    $\square$
\end{flushright}

\paragraph{Proof of bulk duality \eqref{edgeDualRealtion}.}To show this relation we need two 'ingredients'. First the existence of a similarity transformation between the Hamiltonian $\mathcal{H}_{x,y}$  and its transposed. As we will show, this similarity transformation is $R_{x}R_{y}$.  Second, the possibility of finding a symmetry for the edge Hamiltonian. Exploiting \eqref{hamiltonianCasimir}, we can take any symmetry of the Casimir and apply the co-product. As we will see, it will be convenient to choose $\sum_{a=1}^{N-1}E_{aN}$.

We first look for the similarity between $\mathcal{H}_{x,y}$ and its transposed. Using \eqref{transpositionPropertyR} we obtain  
\begin{equation}\label{transpositionPropertyH}
    \mathcal{H}_{x,y}^{T}=\left(R_{x}R_{y}\right)\mathcal{H}_{x,y}\left(R_{x}R_{y}\right)^{-1}
\end{equation}
therefore we have found the similarity transformation between $\mathcal{H}_{x,y}$ and its transposed. \\
We now look for a symmetry of $\mathcal{H}_{x,y}$, i.e. a matrix $S_{x,y}$ of the same dimension such that it satisfies 
\begin{equation}
	\mathcal{H}_{x,y}S_{x,y}=S_{x,y}\mathcal{H}_{x,y}
	%\quad \Leftrightarrow \quad [\mathcal{H}_{x,y},S_{x,y}]=0
	\dt
\end{equation}
Using \eqref{hamiltonianCasimir}, we observe that $\mathcal{H}_{x,y}$ is proportional to the coproduct of the second Casimir, up to a diagonal term. Therefore, it is enough to look for a symmetry of $\Delta (C)$. Using the bilinearity of the coproduct operator and the fact that $C$ belongs to the centre of the Lie algebra, it is easy to show that for any matrix $E\in gl(N)$ the following holds:
\begin{equation}
 \text{if } \quad	[C,E]=0\qquad  \text{ then }\qquad \left[\Delta (C),\Delta(E)) \right]=0\dt
\end{equation}
We chose 
\begin{equation}
	E=\sum_{a=1}^{N-1}E_{aN}
\end{equation}
and, for a fixed $(x,y)\in \mathcal{E}$, we define
\begin{equation}
	S_{x,y}=\exp{(\Delta_{x,y}(E))}=\exp{(E^{x})}\exp{(E^{y})}
\end{equation}
where $\Delta_{x,y}(E)$ is a copy of the coproduct acting on sites $x$ and $y$. As a consequence, this operator $S_{x,y}$ satisfies
\begin{equation}\label{symmetryH}
	\left[S_{x,y},\mathcal{H}_{x,y}\right]=0
\end{equation}
i.e. it is a symmetry of $\mathcal{H}_{x,y}$. Exploiting these considerations we may write
